\thetitle

### 2013-04-13 tfpie/tfpie.tex
Fix to local bib.

\title{From Principles to Practice with Class in the First Year}
\author{Sam Tobin-Hochstadt \quad\qquad David Van Horn
\institute{Northeastern University\\
Boston, Massachusetts, USA}
\email{\{samth,dvanhorn\}@ccs.neu.edu}
}
\def\titlerunning{A Longtitled Paper}
\def\authorrunning{S. Tobin-Hochstadt \& D. Van Horn}
\begin{document}
\maketitle

@@

@@

@@

% \nocite{*}
\bibliographystyle{eptcs}
\bibliography{dvh-bibliography}
\end{document}

>>>>

\newcommand\thetitle{From Principles to Practice with Class in the First Year}

\title{\thetitle}
\author{Sam Tobin-Hochstadt \quad\qquad David Van Horn
\institute{Northeastern University\\
Boston, Massachusetts, USA}
\email{\{samth,dvanhorn\}@ccs.neu.edu}
}
\def\titlerunning{\thetitle}
\def\authorrunning{S. Tobin-Hochstadt \& D. Van Horn}
\begin{document}
\maketitle

@@

As an example, Northeastern University teaches functional programming
in the first semester using \emph{How to Design Programs}
\cite{dvanhorn:Felleisen2001How}, followed by object-oriented
programming using \emph{How to Design Classes} \cite{local:htdc} in
the second semester.  This sequence is one

These two courses are tightly integrated
and have been taught by the designers of this cirriculum.

@@

\cite{local:dpc}

@@

\cite{local:htdc}

% \nocite{*}
\bibliographystyle{eptcs}
\bibliography{dvh-bibliography,local}
\end{document}
